Supplementary Materials

### 2021-01-12 analysis/analysis.Rmd
fixed some typos in sup mat

We will remove identity relationships (i.e., a group is a subgroup of itself) and the three pairs of wallpapers groups that it subgroups of each other (e.g., PM is a subgroup of CM, and CM is a subgroup of PM). This leaves us with a total of `r nrow(subgroups)` subgroups to include in our analysis.

@@

*  Use weakly-informative priors.
*  Fit a multi-level model using the lognormal distribution.
  + independent variable (wallpaper group) and one dependent variable (rms or threshold).
  + maximal random effect structure.
* Check model fit (r̂ statistics and trace plots).
* Extract mcmc samples from the posterior distributions.
* Use these samples to estimate the difference between sub- and supergroups.

@@

Our independent variable is a categorical factor with 16 levels. We will drop the intercept from our model and instead fit a coefficent for each factor level ($y \sim x - 0$). As our dependant variable will be log-transformed, we can use the priors below:

@@

We can see that i) our priors are relatively weak as the predictions span several orders of magnitide, and ii) our empirical data falls within this range.

@@

comparison_summary <- function(subgroup_comp_dat, greater, measurement_lab) {
  # compute probabilties
  subgroup_comp_dat %>%
    group_by(key, index, normal) %>%
    summarise(
      mean_value = mean(value),
      prob_one_tailed = if_else(greater == TRUE, mean(value > 0), mean(value < 0)),
      .groups = "drop")  %>%
    mutate(
      prob_one_tailed = if_else(prob_one_tailed==0, 0.01, prob_one_tailed),
      measurement = measurement_lab,
      index_labs = as.numeric(as.factor(index)),
      lab_cols = v_cols[index_labs],
      prob_cat = cut(prob_one_tailed, c(0, 0.5, 0.75, 0.9, 0.99, 1))) -> comp_summary_dat

@@

# compute probabilties
comp_summary$eeg <- comparison_summary(subgroup_comp$eeg, TRUE, 'rms')

@@

# compute probabilties
comp_summary$threshold <- comparison_summary(subgroup_comp$threshold, FALSE, 'threshold')

@@

# compute probabilties
comp_summary$occ_even <- comparison_summary(subgroup_comp$occ_even, TRUE, 'rms')

@@

# compute probabilties
comp_summary$par_odd <- comparison_summary(subgroup_comp$par_odd, TRUE, 'rms')

@@

If we take $p$=0.95 as our cut-off, we can see that the subgroup relations are preserved in 56/63 = 89% and 49/64 = 78% of the comparisons for the primary SSVEP and display durations repectively. This compares to the 32/64= 50% and 22/64 = 35% for the control SSVEP conditions.

@@

We will also investigate if we see the corresponding pattern with the display duration threshold data, with the time taken to detect the symmetry dreasing as we increase the amount of rotational symmetry.

>>>>

We will remove identity relationships (i.e., a group is a subgroup of itself) and the three pairs of wallpapers groups that are subgroups of each other (e.g., PM is a subgroup of CM, and CM is a subgroup of PM). This leaves us with a total of `r nrow(subgroups)` subgroups to include in our analysis.

@@

*  Use weakly-informative priors.
*  Fit a multi-level model using the lognormal distribution.
  + independent variable (wallpaper group) and one dependent variable (rms or threshold).
  + maximal random effect structure.
* Check model fit ($r^2$ statistics and trace plots).
* Extract mcmc samples from the posterior distributions.
* Use these samples to estimate the difference between sub- and supergroups.

@@

Our independent variable is a categorical factor with 16 levels. We will drop the intercept from our model and instead fit a coefficient for each factor level ($y \sim x - 0$). As our defendant variable will be log-transformed, we can use the priors below:

@@

We can see that i) our priors are relatively weak as the predictions span several orders of magnitude, and ii) our empirical data falls within this range.

@@

comparison_summary <- function(subgroup_comp_dat, greater, measurement_lab) {
  # compute probabilities
  subgroup_comp_dat %>%
    group_by(key, index, normal) %>%
    summarise(
      mean_value = mean(value),
      prob_one_tailed = if_else(greater == TRUE, mean(value > 0), mean(value < 0)),
      .groups = "drop")  %>%
    mutate(
      prob_one_tailed = if_else(prob_one_tailed==0, 0.01, prob_one_tailed),
      measurement = measurement_lab,
      index_labs = as.numeric(as.factor(index)),
      lab_cols = v_cols[index_labs],
      prob_cat = cut(prob_one_tailed, c(0, 0.5, 0.75, 0.9, 0.99, 1))) -> comp_summary_dat

@@

# compute probabilities
comp_summary$eeg <- comparison_summary(subgroup_comp$eeg, TRUE, 'rms')

@@

# compute probabilities
comp_summary$threshold <- comparison_summary(subgroup_comp$threshold, FALSE, 'threshold')

@@

# compute probabilities
comp_summary$occ_even <- comparison_summary(subgroup_comp$occ_even, TRUE, 'rms')

@@

# compute probabilities
comp_summary$par_odd <- comparison_summary(subgroup_comp$par_odd, TRUE, 'rms')

@@

If we take $p$=0.95 as our cut-off, we can see that the subgroup relations are preserved in 56/63 = 89% and 49/63 = 78% of the comparisons for the primary SSVEP and display durations respectively. This compares to the 32/63= 51% and 22/63 = 35% for the control SSVEP conditions.

@@

We will also investigate if we see the corresponding pattern with the display duration threshold data, with the time taken to detect the symmetry decreasing as we increase the amount of rotational symmetry.
